Astr 513: Final Project

### 2016-05-09 Final_Project/ms.tex
Wrote about half of results section

\section{Results}
\label{sec:results}

>>>>

\section{Results}
\label{sec:results}
The most likely values and uncertainties of $\Omega_M$ and $h$ 
in a $\Lambda$CDM model are listed in \autoref{tab:lcdm}. Included are results from
using the \citet{betoule2014} and \citet{rest2014} data with and without the addition 
of \Planck priors. Additionally, the 68\% and 95\% confidence contours can be seen
in \autoref{fig:betoule_lcdm_corner} and (Rest's corner plot if available).

Similary, \autoref{tab:wcdm}, \autoref{fig:betoule_wcdm_corner}, and \autoref{fig:rest_wcdm_corner}
detail the most likely values and confidence intervals of $\Omega_M$, $h$, and $w$ 
in a $w$CDM model. An extra entry is given in \autoref{tab:wcdm} for just our prior, the 
\Planck likelihood. 
\LC{Not done yet}
